---
title: "Running from Trex"
author: "Nick Borcherding"
date: "7/6/2021"
output: html_document
---

```{r}
library(stringr)
library(stringdist)
library(amap)
library(dplyr)
library(muxViz)
library(igraph)
tmp <- readRDS("~/Documents/GitHub/Trex/Sample11_seuratObject.rds")
reference <- read.delim("~/Documents/GitHub/Trex/data/aa_props.tsv")
#igraph <- runTrex(tmp)

source("~/Documents/GitHub/Trex/R/metrics.R")
source("~/Documents/GitHub/Trex/R/utils.R")
source("~/Documents/GitHub/Trex/R/runTrex.R")

meta <- tmp[[]]
meta <- meta[!is.na(meta$cloneType),]
tmp <- subset(tmp, cells = rownames(meta))

#sce <- as.SingleCellExperiment(tmp)

eigen <- maTrex(tmp, AA.method = "mean", nearest.method = "threshold")
plot(eigen[,1], eigen[,2])

tmp <- runTrex(tmp, AA.method = "mean", nearest.method = "threshold")

plot(tmp@reductions$Trex[,2], tmp@reductions$Trex[,3])
```


#Notes:

As of right now the following works to produce PCA that can be added to the seurat object and perform WNN on

Issues: 
1. Eigen vectors after 1d are not helpful
 - So this is not the case the first eigenvector actually is representative of the large issue of NA values vs non-NA-value, eliminating the first eigen dimension recovers the better seperation of clones
2. The WNN actually adds T cells to non-T cell and non T cells form two majory clusters that are a mix of T/B/and myeloid

Things I have Tried:
- Change the ARPACK to call largest algebraic value (not helpful)
- Change the assay call in DimReduction creation of Trex
- What happens with lower thresholds vs higher thresholds? - Changes the vector not the eigen values
-Remove non-T cells? Still mixing of CD4 and CD8 T cells (this might change wehn adding additional metrixs)

Guess
- Change nature of multiplexed list
    - What if threhsold is emilimated and graphs are made by raw distance calc?
    - Any change if we remove the diagnols?

    
```{r}

unwanted_genes <- "^IGHV*|^IGHJ*|^IGHD*|^IGKV*|^IGLV*|^TRBV*|^TRBD*|^TRBJ*|^TRDV*|^TRDD*|^TRDJ*|^TRAV*|^TRAJ*|^TRGV*|^TRGJ*"
remove_genes <- tmp[["RNA"]]@var.features %in% unwanted_genes
tmp[["RNA"]]@var.features = tmp[["RNA"]]@var.features[!remove_genes]

tmp <- FindNeighbors(tmp)
tmp <- FindNeighbors(tmp, reduction = "Trex")
wnn  <- FindMultiModalNeighbors(
  tmp, 
  reduction.list = list("pca", "Trex"), 
  dims.list = list(1:30, 1:20), 
  modality.weight.name = "RNA.weight"
)

tmp <- RunUMAP(wnn, nn.name = "weighted.nn", reduction.name = "wnn.umap", reduction.key = "wnnUMAP_")
tmp <- RunUMAP(tmp, reduction = 'pca', dims = 1:30, assay = 'RNA', 
              reduction.name = 'rna.umap', reduction.key = 'rnaUMAP_')
tmp <- RunUMAP(tmp, reduction = 'Trex', dims = 1:20, 
              reduction.name = 'trex.umap', reduction.key = 'trexUMAP_')
tmp <- FindClusters(tmp, graph.name = "wsnn", algorithm = 3, verbose = FALSE)


DimPlot(tmp, reduction = 'Trex', dims = c(2,3))


FeaturePlot(tmp, reduction = 'rna.umap', features = "CD3G")
FeaturePlot(tmp, reduction = 'rna.umap', features = "CD4")
FeaturePlot(tmp, reduction = 'rna.umap', features = "CD8A")
DimPlot(tmp, reduction = 'rna.umap', group.by = "cloneType")
DimPlot(tmp, reduction = 'trex.umap')
FeaturePlot(tmp, reduction = 'trex.umap', features = "CD3G")
FeaturePlot(tmp, reduction = 'trex.umap', features = "CD4")
FeaturePlot(tmp, reduction = 'trex.umap', features = "CD8A")
DimPlot(tmp, reduction = 'wnn.umap')
FeaturePlot(tmp, reduction = 'wnn.umap', features = "CD3G")
FeaturePlot(tmp, reduction = 'wnn.umap', features = "CD4")
FeaturePlot(tmp, reduction = 'wnn.umap', features = "CD8A")
FeaturePlot(tmp, reduction = 'wnn.umap', features = "FOXP3")
DimPlot(tmp, reduction = 'wnn.umap', group.by = "cloneType")
DimPlot(tmp, reduction = 'wnn.umap')
```

```{r}
plot(eigen[,3], eigen[,2])
```


```{r}
h2o.init()
x <- int
#y <- matrix(ncol = (80-nrow(x)), nrow = 28)
y <- matrix(nrow = (80-nrow(x)), ncol = 28)
colnames(y) <- colnames(x[,2:29])
#x <- cbind(t(x[,2:29]), y)
x <- rbind(x[,2:29], y)
h2o.init()
z <- as.h2o(x)
ae1 <- h2o.deeplearning(
  x = seq_along(z), 
  training_frame = z,
  autoencoder = TRUE,
  hidden = c(100,50,30, 1, 30 ,50,100), 
  activation = "Tanh",
  seed = 123
)

ae1_coding <- h2o.deepfeatures(ae1, z, layer = 1)
ae2_coding <- h2o.deepfeatures(w1, w1, layer = 1)

ae2 <- h2o.deeplearning(
  x = ae1_coding, 
  training_frame = ae1_coding,
  autoencoder = TRUE,
  hidden = 2, 
  activation = "Tanh",
)

layers <- c(100,50,20)
  args <- list(activation="Tanh", epochs=1, l1=1e-5)
  ae <- get_stacked_ae_array(z, layers, args)
  
w1 <- as.matrix(h2o.deepfeatures(ae1, final.hex, layer=4))
names(w1) <- gsub("DF", paste0("L",2,sep=""), names(z)) 
w2 = h2o.deepfeatures(ae[[2]], w1, layer = 1)
rownames(w1) <- int$aa
plot(w1)

get_stacked_ae_array <- function(training_data,layers,args){  
    vector <- c()
    index = 0
    for(i in 1:length(layers)){    
      index = index + 1
      ae_model <- do.call(h2o.deeplearning, 
                          modifyList(list(x=names(training_data),
                                          training_frame=training_data,
                                          autoencoder=TRUE,
                                          hidden=layers[i]),
                                     args))
      training_data = h2o.deepfeatures(ae_model,training_data,layer=1)
      
      names(training_data) <- gsub("DF", paste0("L",index,sep=""), names(training_data)) 
      vector <- c(vector, ae_model)    
    }
    vector
  }
```



